Outline

### 2017-07-24 Outline.Rmd
Update Outline.Rmd

### Educational problem solved
+ Interactive platform to learn coding, with built in assistance and checks for understanding

@@

### Comparison and contrast with competing technologies  
+ Swirl lessons
+ 'Try R' by Code School 
+ Anything else?

>>>>

### Educational problem solved
+ Interactive platform to learn coding, with built in assistance and checks for understanding
+ User-friendly interface, unlike Swirl's interface which can be daunting for students who have never seen R

@@

### Comparison and contrast with competing technologies  
+ Swirl lessons
+ 'Try R' by Code School--> interactive platform but not reproducible
+ Anything else?
